\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-25 paper/algorithm.tex
paper: reworked motivation section
paper: some proof cleanup

\begin{definition}
An abstract imputation operator $I: \mathcal{P}(String) \rightarrow \mathcal{P}(\{ \delta, \mu \})$ is a function that given a dirty set maps to
a set of imputation operations. For convenience we denote applying the set of transformations to a plan $p$ as $I(p)$ and understand that this
is shorthand for $\{ op(p)   | op \in I(\textsc{Dirty}(p)) \}$.
\end{definition}

Algorithm{~\ref{algo:top-level-planner} plans the query in stages. It first handles any pushed-down selections, it then optimizes joins, then groupby/aggregations,
and finally projections. It maintains all necessary state information through a combination of dirty sets on intermediate plans and
initializing empty plan caches at stages that require it. Given this, we can succinctly describe possible transformations to a plan at a given
point in the algorithm solely through $I$.

@@

\begin{figure}
\begin{tikzpicture}
% before I
\node(p1) {$p_1$};
\node[right=of p1](dom1){$\prec$};
\node[right=of dom1](p2) {$p_2$};

>>>>

\begin{definition}
$I: \mathcal{P}(D) \rightarrow \mathcal{P}(\{ \delta, \mu \})$, where
$D$ is the set of dirty attributes for a relation, is an abstract imputation operator mapping a set of dirty
attributes to a set of imputation operations.

For convenience we denote applying the set of imputation operations to a plan $p$ as $I(p)$ and understand that this
is shorthand for $\{ op(p)   | op \in I(\textsc{Dirty}(p)) \}$.
\end{definition}

We can succinctly describe possible imputation transformations to a plan at a given point in the planning algorithm solely through $I$.

@@

\begin{figure}
\centering
\begin{tikzpicture}
% before I
\node(p1) {$p_1$};
\node[right=of p1](dom1){$\prec$};
\node[right=of dom1](p2) {$p_2$};
